---
title: "Coursera - Developing data products - Final assignement week 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## App function

The shiny app is based on the RStudio mtcars datatset. It shows the correlation between the fuel consumption (mpg) vs. different car parameters. By using the app you are able to figure out the influence of these different parameters on the mpg value.
You will find the app under the following link:
https://sacool117.shinyapps.io/Fuel-consumption/



```{r, echo=TRUE}
head(mtcars)
```


## UI Code


```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}

library(shiny)



shinyUI(fluidPage(

  # App title

  titlePanel("Mtcars Dataset - Fuel consumption"),

  sidebarPanel(

    selectInput("value", "Value:", 

                c("Cylinders" = "cyl",
                  "Horsepower" = "hp",
                  "Weight" = "wt",
                  "Acceleration 1/4 mile time" = "qsec",
                  "Number of forward gears" = "gear"
                  ))
  ),

  mainPanel(

    plotOutput("mpgPlot")

  )

))

```


## Server Code


```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}

library(shiny)

library(plotly)

mpgData <- mtcars

shinyServer(function(input, output) {


 output$mpgPlot <- renderPlot({

    ggplot(mpgData, aes_string(y=input$value, x="mpg")) + geom_point()

  })

  

})

```
